\documentclass{beamer} 
\usepackage{amsmath,amsthm}
\usepackage{graphicx,microtype,parskip}
\usepackage{caption,subcaption,multirow}
\usepackage{attrib}

\frenchspacing

\usetheme{default}
\usecolortheme{whale}

\setbeamertemplate{navigation symbols}{}

\setbeamercolor{title}{fg=blue,bg=white}

\setbeamercolor{block title}{fg=white,bg=gray}
\setbeamercolor{block body}{fg=black,bg=lightgray}

\setbeamercolor{block title alerted}{fg=white,bg=darkgray}
\setbeamercolor{block body alerted}{fg=black,bg=lightgray}

\AtBeginSection[]
{
  \begin{frame}
    \tableofcontents[currentsection]
  \end{frame}
}


\title{Gambling with Australian brachiopods}
\author{Peter D Smits}
\institute{Committee on Evolutionary Biology, University of Chicago}

\begin{document}

\begin{frame}
  \maketitle
\end{frame}

\begin{frame}
  \frametitle{Extinction}

  \begin{quotation}
    All species that have ever lived are, to a first approximation, dead.

    \tiny{\attrib{Raup 1986 \underline{The Nemesis Affair}}}
  \end{quotation}
\end{frame}

\begin{frame}
  \frametitle{Foundation}

  \begin{alertblock}{Question}
    Why do certain taxa go extinct at different rates?
  \end{alertblock}
\end{frame}

\begin{frame}
  \frametitle{Modes of extinction}

  \hspace{\stretch{0.4}} Field of Bullets 
  \hspace{\stretch{0.5}} \textbf{--} 
  \hspace{\stretch{0.5}} Wanton 
  \hspace{\stretch{0.5}} \textbf{--} 
  \hspace{\stretch{0.5}} Fair Game 
  \hspace{\stretch{1}}

  \bigskip

  \tiny{\attrib{Raup 1991 \underline{Extinction: Bad Genes or Bad Luck?}}}
\end{frame}

\begin{frame}
  \frametitle{Common observation}

  \begin{block}{Known pattern}
    Species with large geographic ranges have a low extinction risk.
  \end{block}

  \bigskip

  \begin{center}
    Expected given \alert{purely random} extinction.
  \end{center}
\end{frame}


\begin{frame}
  \frametitle{Gambler's Ruin}

  \begin{definition}
    Given infinite time, all gambler's go bust. The rate is proportional to starting chip count.
  \end{definition}

  \bigskip

  \begin{center}
    \begin{align*}
      \text{Gambler} &\equiv \text{Taxon} \\
      \\
      \text{Chip count} &\equiv \text{Range, Species:Genus, etc.}
    \end{align*}
  \end{center}
  
\end{frame}


% Stochastic expectations of extinction and the Gambler's Ruin


% Ecology and interactions with the environment


% Enter Brachiopods


% Preliminary analytical framework


% Results


% Future modeling



\end{document}
